Our Galactic Midplane Is Probably Wrong, and Not by a Little

### 2019-02-04 paper/ms.tex
Add barebones conclusion
Add orbit plot to appendix

@@

\appendix \section{Appendix 1}
Gonna write an appendix probably

>>>>

\section{Conclusions}\label{sec:conclusion}
Let's conclude, shall we.

\begin{itemize}
\item

\end{itemize}

@@

\appendix
\section{Orbits} \label{app:orbits}
We plot the three orbits considered throughout the work
(Table~\ref{tab:orbits}) in Figure~\ref{fig:plot_orbits}.

\begin{figure*}
\plotone{fig/orbits.pdf}
\caption{The three orbits presented in Table~\ref{tab:orbits} and considered
throughout the work. We plot the thin, thick, and halo orbits in the {\em
left}, {\em center}, and {\em right} columns, respectively. The {\em upper}
row shows a plot of $x$ vs. $y$ while the {\em lower} row shows $R$ vs. $z$.}
\label{fig:plot_orbits}
\end{figure*}
